Proposed Solution

### 2017-04-17 OOPSLA17/secs/related.tex
vericonf: related work for tianyin's PCheck

>>>>

PCheck~\cite{xu16early} aims to add configuration checking code to
the system source code by emulating potential commands and behaviors
of the system. However, PCheck is limited to the reliability problems
caused by misconfiguration parameters; on the contrary, 
\app can cover general misconfiguration issues 
including performance, security, availability and reliability.
In addition, PCheck's emulation capability heavily depends on 
system category and source code.
For example, for some systems (\eg, ZooKeeper) whose behaviors are 
hard to emulate, PCheck cannot automatically generate the corresponding
checking code; on the contrary, \app does not rely on specific
system behaviors or source code.
